Project 1 Checkpoint

### 2015-02-03 project1/checkpoint/main.tex
Talking about the data analysis tools

So, instead we'll take a simpler approach and assume the ``true distribution`` is modeled by what was observed,
and simply use the observed frequency distribution as our input distribution. As the project progresses we can
refine this model.

@@

@@

\section{Simulation Software Architecture}
Simulation Software

>>>>

Given the difficulties with modelling we'll take a simpler approach and assume the ``true distribution`` is modeled by what was observed,
and simply use the observed frequency distribution as our input distribution. As the project progresses we can
refine this model.

@@

\subsubsection{Data Analysis}
In the \texttt{data\_processing} folder, most of code used for distribution fitting and statistics can be found there.
The data analysis code was written in Javascript, and runs completely in NodeJS \cite{nodejs}. NPM \cite{npm} was used
to manage dependencies and those dependencies can be seen in the \texttt{package.json} file. Of those packages, I have
authored the \texttt{chi-squared-test} module \cite{chiSquaredNpm}, and the \texttt{gamma-distribution}
\cite{gammaDistributionNpm}. Gulp \cite{gulp} was used a build tool for automating tasks (including building this paper).

@@

\section{Simulation Software Architecture}
The simulation software attempts to utilize
